Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-07-04 prop_iop.tex
prop_letter.tex Updating...

\begin{definition}A mixed state\nb$\rho$ is called totally mixed
if it satisfies the following conditions.
\begin{itemize}
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
\end{itemize}
\end{definition}

>>>>

\begin{definition}A mixed state\nb$\rho$ is called totally mixed
if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.\end{definition}

### 2017-07-04 prop_letter.tex
prop_letter.tex Updating...

Although Gleason's theorem doesn't hold for every quantum IVPM, it
can be applied in a limit case when the intervals are infinitely precise.
That is, when $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum IVPM can be recast as an real-valued one and has a unique
state consistent with it on every projector when $d\ge3$.

>>>>

Although Gleason's theorem doesn't hold for every quantum IVPM, if
a quantum IVPM\nb$\bar{\mu}$ is induced by a totally mixed state\nb$\rho$
nicely, then whether another density matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$
can be estimated by $\left\Vert \rho-\rho'\right\Vert $, where a
state\nb$\rho$ is called totally mixed if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
and the the norm of a matrix\nb$A$ is defined by $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
For example, consider the intervals\nb$\widehat{\mathscr{I}}_{n}=\set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\cup\left\{ \left[0,0\right],\left[1,1\right]\right\} $
which are overlapping intervals with length\nb$1/n$ except the intervals
near the ends. We can define an interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
by the following:
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
\item when $0<x<1$, we have $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by either one of the following:
\begin{itemize}
\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
\item $2\nmid k$ and $k-0.5<2nx<k+0.5$.
\end{itemize}
\end{itemize}
Then, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM, and we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
In summary, the states consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will be closer and closer to $\rho$ as $n$ goes to infinity. In
a limit case when the intervals are infinitely precise, i.e., $\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum IVPM can be recast as an real-valued one and has a unique
state consistent with it on every projector when $d\ge3$.
